peters_elements_causal_inference

### 2021-04-25 paper/draft.Rmd
notes

>>>>

The first principle is independence of our mechanisms.
As a reminder, each equation in a SCM is a separate independent mechanism.
In a two-variable case of a causal model one can differentiate between the cause distribution and the effect distribution(Peters et al.,2017).

Implications:

1. Change mechanism without changing the rest of the model 
2. Change of one mechanism does not contain information on other changes
3. Systems can never be isolated from environment, henceforth weak dependence of noise possible without violating assumption about independent mechanisms

### 2021-04-25 references/peters_Causality.Rmd
xyz
notes

SCM somewhere betweren mechanisitic model with differential equations and statistical model

@@

>>>>

SCM somewhere between mechanisitic model with differential equations and statistical model

@@

SEM vs SCM: SEM: Algebraic equations rather than assignments from CS in SCM

Independent mechanisms

Autonomous modules
in Case example between cause distribution and effect distribution.

Confusion economics + statistics

Economics = E(Y|do(x)) - claim stats no substance 
Statistics =E(Y|x) - claim SE have no meaning
